Unified treatment of the asymptotics of asymmetric kernel density estimators

### 2015-12-17 paper/paper.tex
Added makefile for paper.
Fixed erroneous figure caption.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage[backend=bibtex,style=numeric,sorting=none,firstinits=true]{biblatex}
\addbibresource{/Users/tillhoffmann/google_drive/papers/library.bib}
\usepackage[foot]{amsaddr}

@@

\caption{\label{fig:improper-gamma}Density estimate of $n=300$ samples drawn from a log-normal distribution with logarithmic mean $\mu=1$ and logarithmic variance $\Sigma^{2}=1$ using an improper gamma estimator (solid black line) and a Gaussian approximation (dashed black line). The generating distribution is shown as a dotted black line and individual samples are shown as markers on the horizontal axis. The bandwidth for both estimators was obtained using the plugin expression in Eq.~\eqref{eq:chen-plugin} which minimises the MISE in Eq.~\eqref{eq:chen-lognormal-mise} as shown in Figure~\ref{fig:bandwidth-comparison}.}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage[backend=bibtex,style=numeric,sorting=none,firstinits=true]{biblatex}
\addbibresource{paper.bib}
\usepackage[foot]{amsaddr}

@@

\caption{\label{fig:improper-gamma}Density estimate of $n=300$ samples drawn from a log-normal distribution with logarithmic mean $\mu=1$ and logarithmic variance $\Sigma^{2}=1$ using an improper gamma estimator (solid black line) and a Gaussian approximation (dashed black line). The generating distribution is shown as a dotted black line and individual samples are shown as markers on the horizontal axis. The bandwidth for both estimators was obtained using the plugin expression in Eq.~\eqref{eq:chen-plugin} which minimises the MISE in Eq.~\eqref{eq:chen-lognormal-mise}.}
\end{figure}
